TUGAS POLINOMIAL CHAPTER 15

### 2021-10-12 Semester I/Pemrograman dalam Sains/Minggu VIII/pr.Rmd
15.2

```{r,echo=FALSE}
data = read.csv("15_1.csv")
data
```

@@

@@

>>>>

```{r,echo=FALSE}
data = read.csv("15_1.csv")
colnames(data) = c("j","x[j]","y[j]")
data
```

@@

```{r out.width = "100%",echo=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.cap = "Gambar 15.2"}
knitr::include_graphics("15_2.png")
```

```{r,echo=FALSE}
data = read.csv("15_2.csv")
colnames(data) = c("j","x[j]","y[j]")
data
```

```
The roots:
[-1.14869835+0.j  -0.35496731-1.09247706j -0.35496731+1.09247706j
  0.92931649-0.67518795j  0.92931649+0.67518795j]
```

@@

```{r,echo=FALSE}
data = read.csv("15_1.csv")
colnames(data) = c("j","x[j]","y[j]")
data
```
